Automated discovery of interpretable gravitational-wave population models

### 2022-06-27 src/tex/ms.tex
Somehow the running title is off

%%%%%%%% ICML 2022 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

\documentclass[nohyperref]{article}
\usepackage{showyourwork}

@@

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
%\icmltitlerunning{Automated discovery of interpretable gravitational-wave population models}

@@

\twocolumn[
%\icmltitle{Automatic, Flexible and Interpretable:\\gravitational-wave population analysis with symbolic regression}
%\icmltitle{Automated discovery of symbolic gravitational-wave population models}
\icmltitle{Automated discovery of interpretable gravitational-wave population models}

\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Kaze W.K Wong}{equal,yyy}
\icmlauthor{Miles Cranmer}{equal,yyy,comp}
\end{icmlauthorlist}

\icmlaffiliation{flatiron}{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010, USA}

@@

\section{Introduction}
% \begin{figure*}[hbt!]
% % \includegraphics[width=\textwidth]{figures/GWTC3_m1_combined.pdf}
% \includegraphics[width=\textwidth]{figures/Page2.pdf}
% \caption{An illustration of our proposed pipeline, which first
% (\textit{far left})
% requires observations of individual source properties (here, events shown from GWTC3);
% then
% (\textit{middle left}) 
% infers the deconvolved population posterior density;
% followed by (\textit{middle right})
% using symbolic regression to search for an
% an analytic model which approximates the density, using
% operators common to existing population models; and finally
% (\textit{far right}) distilling physical insights
% from the recovered population model.
% }
% %\caption{\textit{left}: posterior density of the primary mass from all events reported in GWTC3. Each line is the normalized posterior density for one event.
% %\textit{middle}: posterior predictive distribution of the Gaussian mixture model reported in \cite{LIGOScientific:2021psn}.
% %\textit{right}: equations tabulated in table \ref{tab:equations}}
% \label{fig:Gaussian_m1_fit}
% \end{figure*}
The rate of gravitational wave (GW) detections increases exponentially as the sensitivity of GW detectors improves \cite{LIGOScientific:2021djp} since the discovery in 2015 \cite{Abbott:2016blz}.
To date, there are 79 officially announced events, the majority of them being binary black holes (BBH).
With the increasing number of observed GW events, more and more features in the distribution of GW events await to be discovered.
Currently, one of the most common ways to understand the observed GW population is through phenomenological modeling.
For example, to understand the distribution of primary mass in observed BBHs, one would write down a hand-crafted model of the primary mass distribution, such as a power-law distribution \cite{LIGOScientific:2021psn}.
By comparing the model to the data, one can measure the parameters which characterize the model, such as the spectral index of a power-law distribution.

@@

% \bibliographystyle{icml2022}
\bibliography{bib.bib}

>>>>

\documentclass[nohyperref]{article}
\usepackage{aas_macros}
\usepackage{showyourwork}

@@

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:

\icmltitlerunning{Short}

@@

\twocolumn[
\icmltitle{Automated discovery of interpretable gravitational-wave population models}

\begin{icmlauthorlist}
\icmlauthor{Kaze W.K Wong}{flatiron}
\icmlauthor{Miles Cranmer}{princeton}
\end{icmlauthorlist}

\icmlaffiliation{flatiron}{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010, USA}
\icmlaffiliation{princeton}{Department of Astrophysical Sciences, Princeton University, Princeton, New Jersey 08544, USA}

@@

\section{Introduction}
\begin{figure*}[hbt!]
% \includegraphics[width=\textwidth]{figures/GWTC3_m1_combined.pdf}
% \includegraphics[width=\textwidth]{figures/Page2.pdf}
\caption{An illustration of our proposed pipeline, which first
(\textit{far left})
requires observations of individual source properties (here, events shown from GWTC3);
then
(\textit{middle left}) 
infers the deconvolved population posterior density;
followed by (\textit{middle right})
using symbolic regression to search for an
an analytic model which approximates the density, using
operators common to existing population models; and finally
(\textit{far right}) distilling physical insights
from the recovered population model.
}
%\caption{\textit{left}: posterior density of the primary mass from all events reported in GWTC3. Each line is the normalized posterior density for one event.
%\textit{middle}: posterior predictive distribution of the Gaussian mixture model reported in \cite{LIGOScientific:2021psn}.
%\textit{right}: equations tabulated in table \ref{tab:equations}}
\label{fig:Gaussian_m1_fit}
\end{figure*}
The rate of gravitational wave (GW) detections increases exponentially as the sensitivity of GW detectors improves \cite{LIGOScientific:2021djp} since the discovery in 2015 \cite{Abbott:2016blz}.
To date, there are 79 officially announced events, the majority of them being binary black holes (BBH).
With the increasing number of observed GW events, more and more features in the distribution of GW events await to be discovered.
Currently, one of the most common ways to understand the observed GW population is through phenomenological modeling.
For example, to understand the distribution of primary mass in observed BBHs, one would write down a hand-crafted model of the primary mass distribution, such as a power-law distribution \cite{LIGOScientific:2021psn}.
By comparing the model to the data, one can measure the parameters which characterize the model, such as the spectral index of a power-law distribution.

@@

\bibliographystyle{icml2022}
\bibliography{bib}
